Kaggle-in-class Data Challenges Can Boost Student Learning

### 2020-07-21 paper-kaggle.Rmd
Addressing all comments except change in notation for ETC 2420/5242 and MAST90083

quiz <- quiz %>% mutate(unit = as.character(unit))
quiz %>%ggplot(aes(x=unit, y=mean, colour=unit)) +
  geom_point(aes(color=unit), size = 2) +
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, 
                position=position_dodge(.9)) +
  facet_wrap(~quiz)

# Calculate CI 
t <- quiz %>% select(unit,quiz,mean,sd) %>%
      gather(statistics, value, -(quiz:unit)) %>%
      unite(temp, unit, statistics) %>%
      spread(temp, value)
t <- t %>% mutate(mean_dif = `5242_mean` - `2420_mean`,
                  sd = sqrt(`5242_sd`^2/34 + `2420_sd`^2/145),
                  v1 = `5242_sd`^2/34,
                  v2 = `2420_sd`^2/145,
                  v = (v1+v2)^2/(v1^2/(34-1)  + v2^2/(145-1) ),
                  t_q = qt( .975, df=v),
                  lower.CI = mean_dif - t_q*sd,
                  upper.CI = mean_dif + t_q*sd
)   
```

@@

@@

>>>>

quiz <- quiz %>% mutate(unit = as.character(unit)) %>%
  mutate(quiz = factor(quiz, levels = c('Quiz 1','Quiz 2','Quiz 3','Quiz 4','Quiz 5','Quiz 6','Quiz 7','Quiz 8','Quiz 9','Quiz 10','Quiz 11','Quiz Tot')))

quiz %>% ggplot(aes(x=unit, y=mean, colour=unit)) +
  geom_point(aes(color=unit), size = 2) +
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, 
                position=position_dodge(.9)) +
  facet_wrap(~quiz) + 
  labs(y="Score",x="") +
   theme(legend.position = "none")

```{r Monash_quiz_mean_diff, fig.cap = "\\label{fig:Monash_quiz_mean_diff} Mean difference of undergraduate (ETC2420) and postgraduate (ETC5242) students quizes scores and CI.", fig.height=4.5, fig.width=6}

# Calculate CI for the differences in mean
t <- quiz %>% select(unit,quiz,mean,sd) %>%
      gather(statistics, value, -(quiz:unit)) %>%
      unite(temp, unit, statistics) %>%
      spread(temp, value)
t <- t %>% mutate(mean_dif = `5242_mean` - `2420_mean`,
                  sd = sqrt(`5242_sd`^2/34 + `2420_sd`^2/145),
                  v1 = `5242_sd`^2/34,
                  v2 = `2420_sd`^2/145,
                  v = (v1+v2)^2/(v1^2/(34-1)  + v2^2/(145-1) ),
                  t_q = qt( .975, df=v),
                  lower.CI = mean_dif - t_q*sd,
                  upper.CI = mean_dif + t_q*sd
)   
t %>% ggplot(aes(x=factor(quiz, levels = c('Quiz 1','Quiz 2','Quiz 3','Quiz 4','Quiz 5','Quiz 6','Quiz 7','Quiz 8','Quiz 9','Quiz 10','Quiz 11','Quiz Tot')) , 
                 y=mean_dif)) +
  geom_point( size = 2) +
  geom_errorbar(aes(ymin=lower.CI, ymax=upper.CI), width=.2, 
                position=position_dodge(.9)) +
  labs(y="Score",x="") +
   theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r Monash_quiz_CI, fig.cap = "\\label{fig:Monash_quiz_CI} Means and CI bars of undergraduate (ETC2420) and postgraduate (ETC5242) students quizes during the semester.", fig.height=4.5, fig.width=6}

# Calculation CI for each mean

t_5242 <- quiz %>% filter( unit=='5242') %>%
      mutate(t_q = qt( .975, df=(34-1)),
                  lower.CI = mean - t_q*sd/sqrt(34),
                  upper.CI = mean + t_q*sd/sqrt(34))

t_2420 <- quiz %>% filter( unit=='2420') %>%
      mutate(t_q = qt( .975, df=(145-1)),
                  lower.CI = mean - t_q*sd/sqrt(145),
                  upper.CI = mean + t_q*sd/sqrt(145))
t <- bind_rows(t_2420,t_5242)

t %>% ggplot(aes(x=unit, y=mean, colour=unit)) +
  geom_point(aes(color=unit), size = 2) +
  geom_errorbar(aes(ymin=lower.CI, ymax=upper.CI), width=.2, 
                position=position_dodge(.9)) +
  facet_wrap(~quiz) + 
  labs(y="Score",x="") +
   theme(legend.position = "none") 
```

@@

The data sets used in our competitions can be shared with other instructors by request.

@@

Running an experiment in the classroom setting imposes, of course, some limitations. One of them is a relatively small sample size of each group. The other is the need to address the university policies, such as the group assessment approach we took for MAST90083.

One of the major limitations is the ability to include such a control group that it is easy to show that its members are equal to the case group members. In the case of Statistical Thinking subject the control group was taken as the undergraduate students that took this subject. At first, using undergraduate students as a control group for graduate students may be surprising.  However, the experience of teaching this subject over several years and some statistical comparison of the two groups can justify this decision. Undergraduate students that took this subject are strong students. Their performance in other tasks and exam questions, not relevant to the competition, was equivalent to the postgraduate students cohort.
